Quality Definitions of Qualities

### 2019-12-18 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
Updats to comments, fixed typos

\begin{defn} 
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. \oo{definition is checked with Mccall}
\end{defn}

@@

\begin{defn}
  Effort required to test a program to ensure that it performs its intended
  function \citep{McCallEtAl1977}. (As summarized in
  \citet{pressman2005software})\oo{McCall defined this as testability not verifiability}
\end{defn}

\begin{defn}
	The effort required to test a program to ensure that it performs its
	intended function \citep{McCallEtAl1977}. (As summarized in
	\citet{VanVliet2000}.) \oo{similar to \citep{pressman2005software}, this}
\end{defn} \oo{McCall defined this as testability not verifiability}

@@

\begin{defn}
  Validatability of a software is the degree of ease in validating (checking)
  that software meets user needs. \wss{Need a citation} \oo{To be removed, I
    don't have any citation, definition was modified from the definition of
    verifiability}
\end{defn}

@@

\begin{defn}
  Requirements validation examines the specification to ensure that all software
  requirements have been stated unambiguously; that inconsistencies, omissions,
  and errors have been detected and corrected; and that the work products
  conform to the standards established for the process, the project, and the
  product \citep{pressman2005software}.
\end{defn}

@@

Combined definition \ref{PerformanceDefnSelected} and
\ref{PerformanceDefnSelected2}: The degree to which a system or component
accomplishes its designated functions within given constraints, such as speed
(database response times, for instance), throughput ( transactions per second),
capacity (con-current usage loads), and timing (hard real-time
demands). \wss{What is the difference between speed and timing?}

@@

\pmi{I will check if Wiegers discusses the difference between speed and timing.}
\pmi{Wiegers did not discuss this difference.}
\pmi{Speed - change over time; timing - related to specification: when something
	should happen in relation to something else - state transitions}

@@

\begin{defn}
  ``The effort required to learn, operate, prepare input, and interpret output
  of a program'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

\begin{defn}
  ``A software is usable - or user fridendly - if its human users find it easy
  to use'' \citep{ghezzi1991fundamentals}.
\end{defn}

@@

\begin{defn}
  Effort required to locate and fix an error in a program
  \citep{pressman2005software}.
\end{defn}

@@

\begin{defn}
  The effort required to locate and fix an error in an operational program
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.) \wss{It looks
    like \citet{pressman2005software} was using \citet{McCallEtAl1977} for their
    definition.} \wss{PM - can you please look into whether
    \citet{pressman2005software} cite \citet{McCallEtAl1977}?  Do they give a
    reason for dropping the word operational?}  \pmi{Yes,
    \citet{pressman2005software} does cite the relevant section of the textbook
    with \citet{McCallEtAl1977}. While they do not give a reason for
    specifically dropping the word operational, they do indicate that their
    given definition ``is a very limited definition''. Perhaps their intent was
    breadth.}
\end{defn}

@@

Combined Definition \ref{MaintainabilityDefnSelected1} and Definition
\ref{MaintainabilityDefnSelected2}: The ease with which a software system or
component can be modified to correct faults, improve performance or other
attributes, or satisfy new requirements.

@@

\begin{defn} 
  The degree to which a software module or other work product can be used in
  more than one software system \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  Extent to which a program [or parts of a program] can be reused in other
  applications - related to the packaging and scope of the functions that the
  program performs \citep{pressman2005software}.
\end{defn}
\begin{defn} \label{ReusabilityDefnSelected} 
  The extent to which a software component can be used with or without
  adaptation in a problem solution other than the one for which it was
  originally developed \citep{kalagiakos2003non}.
\end{defn}
\begin{defn}
  Reusability is the likelihood a segment of source code that can be used again
  to add new functionalities with slight or no modification
  \citep{sandhu2010survey}.
\end{defn}

\begin{defn}
  The extent to which a program (or parts thereof) can be reused in other
  applications \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
\end{defn}

@@

\begin{defn} \label{PortabilityDefnSelected} 
  Effort required to transfer the program from one hardware and/or software
  system environment to another \citep{pressman2005software}.
\end{defn}

@@

\begin{defn}
  ``The effort required to transfer a program from one hardware and/or software
  environment to another'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

\begin{defn}
  ``The effort required to couple one system with another''
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
\end{defn}

@@

Definition \ref{VisibilitySelected} rephrased: The extent to which all of the
steps and the current status of a software development process are documented
clearly.

@@

\begin{defn}
  The degree to which a full implementation of the required functionality has
  been achieved \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
\end{defn}

@@

\begin{defn}
  The use of uniform design and implementation techniques and notations
  throughout a project \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)
\end{defn}

@@

\begin{defn}
  The ability to link software components to requirements
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
\end{defn}

@@

Verifiability is related to testability, which is defined by McCall et al.\ as
``The effort required to test a program to ensure that it performs its intended
function'' \citep{VanVliet2000}.

>>>>

\begin{defn} 
  The extent to which a program satisfies its specifications and fulfills the
  user's mission objectives \citep{McCallEtAl1977}. \oo{definition is checked
    with Mccall} \wss{Great!  Did you add the Mccall paper to the pub repo?}
\end{defn}

@@

\begin{defn}
  Effort required to test a program to ensure that it performs its intended
  function \citep{McCallEtAl1977}. (As summarized in
  \citet{pressman2005software})\oo{McCall defined this as testability not
    verifiability}  \wss{I believe we discussed at the last meeting separating
    the definitions of verifiability and testability.  Olu, please create a new
    section for testability and appropriately copy and paste from this section to
    populate that one.} \wss{Olu, since you have verified the McCall reference,
    you can remove the pressman reference.}
\end{defn}

\begin{defn}
	The effort required to test a program to ensure that it performs its
	intended function \citep{McCallEtAl1977}. (As summarized in
	\citet{VanVliet2000}.) \oo{similar to \citep{pressman2005software}, this}
\end{defn} \oo{McCall defined this as testability not verifiability}  \wss{Since
  you have verified the McCall reference, we can drop the VanVliet reference.}

@@

@@

\begin{defn}
  Requirements validation examines the specification to ensure that all software
  requirements have been stated unambiguously; that inconsistencies, omissions,
  and errors have been detected and corrected; and that the work products
  conform to the standards established for the process, the project, and the
  product \citep{pressman2005software}.  \wss{Olu, is this definition
    originally from pressman, or should we track down the original source?}
\end{defn}

@@

Combined definition \ref{PerformanceDefnSelected} and
\ref{PerformanceDefnSelected2}: The degree to which a system or component
accomplishes its designated functions within given constraints, such as speed
(database response times, for instance), throughput (transactions per second),
capacity (con-current usage loads), and timing (hard real-time
demands). \wss{What is the difference between speed and timing?}

@@

\pmi{I will check if Wiegers discusses the difference between speed and timing.}
\pmi{Wiegers did not discuss this difference.}
\pmi{Speed - change over time; timing - related to specification: when something
	should happen in relation to something else - state transitions}
\wss{If we need both speed and timing, we should define them.  We aren't
  including accuracy from the IEEE definition.  Is that on purpose?}

@@

\begin{defn}
  ``The effort required to learn, operate, prepare input, and interpret output
  of a program'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)  \wss{Once we have verified McCall said this, we can
    remove the VanVliet reference.}
\end{defn}

\begin{defn}
  ``A software is usable - or user friendly - if its human users find it easy
  to use'' \citep{ghezzi1991fundamentals}.
\end{defn}

@@

\begin{defn}
  Effort required to locate and fix an error in a program
  \citep{pressman2005software}. \wss{Peter, if this is from
    McCall, we should just cite the primary source and remove the pressman
    reference.}
\end{defn}

@@

\begin{defn}
  The effort required to locate and fix an error in an operational program
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.) \wss{It looks
    like \citet{pressman2005software} was using \citet{McCallEtAl1977} for their
    definition.} \wss{PM - can you please look into whether
    \citet{pressman2005software} cite \citet{McCallEtAl1977}?  Do they give a
    reason for dropping the word operational?}  \pmi{Yes,
    \citet{pressman2005software} does cite the relevant section of the textbook
    with \citet{McCallEtAl1977}. While they do not give a reason for
    specifically dropping the word operational, they do indicate that their
    given definition ``is a very limited definition''. Perhaps their intent was
    breadth.} \wss{Peter, please verify the McCall reference definition, and
    then just cite that.  Olu has found the McCall reference, so you shouldn't
    have to search for it.  We can remove both the VanVliet and Pressman
    reference in  preference of the McCall definition.}
\end{defn}

@@

Combined Definition \ref{MaintainabilityDefnSelected1} and Definition
\ref{MaintainabilityDefnSelected2}: The ease with which a software system or
component can be modified to correct faults, improve performance or other
attributes, or satisfy new requirements. \wss{We didn't agree as a group in the
  last meeting on our ``measurement'' term, but I think ease is difficult to
  measure.  Maybe we should rephrase to measuring the effort required?}

@@

\begin{defn} 
  The degree to which a software module or other work product can be used in
  more than one software system \citep{IEEEStdGlossarySET1990}.
\end{defn}
\begin{defn}
  Extent to which a program [or parts of a program] can be reused in other
  applications - related to the packaging and scope of the functions that the
  program performs \citep{pressman2005software}. \wss{Peter, if this is from
    McCall, we should just cite the primary source and remove the pressman
    reference.}
\end{defn}
\begin{defn} \label{ReusabilityDefnSelected} 
  The extent to which a software component can be used with or without
  adaptation in a problem solution other than the one for which it was
  originally developed \citep{kalagiakos2003non}.
\end{defn}
\begin{defn}
  Reusability is the likelihood a segment of source code that can be used again
  to add new functionalities with slight or no modification
  \citep{sandhu2010survey}.
\end{defn}

\begin{defn}
  The extent to which a program (or parts thereof) can be reused in other
  applications \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
  \wss{Peter, if this is from McCall, we should just cite the primary source and
    remove the VanVliet reference.}
\end{defn}

@@

\begin{defn} \label{PortabilityDefnSelected} Effort required to transfer the
  program from one hardware and/or software system environment to another
  \citep{pressman2005software}.  \wss{Peter, if this is from McCall, we should
    just cite the primary source and remove the pressman reference.}
\end{defn}

@@

\begin{defn}
  ``The effort required to transfer a program from one hardware and/or software
  environment to another'' \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)  \wss{Peter, if this is from McCall, we should just
    cite the primary source and remove the VanVliet reference.}
\end{defn}

@@

\begin{defn}
  ``The effort required to couple one system with another''
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)  \wss{Ao, if
    this is from McCall, we should just cite the primary source and remove the
    Van Vliet reference.}
\end{defn}

@@

Definition \ref{VisibilitySelected} rephrased: The extent to which all of the
steps \wss{What are all the steps?} and the current status of a software
development process are documented clearly. \wss{I wonder if rather than
  ``documented clearly'', we should be more abstract and talk about how these
  things can be easily determined.  Documentation is probably how the
  information will be conveyed, but it doesn't have to be how it is done.}

@@

\begin{defn}
  The degree to which a full implementation of the required functionality has
  been achieved \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
  \wss{Ao, if this is from McCall, we should just cite the primary source and
    remove the Van Vliet reference.}
\end{defn}

@@

\begin{defn}
  The use of uniform design and implementation techniques and notations
  throughout a project \citep{McCallEtAl1977}. (As summarized in
  \citet{VanVliet2000}.)  \wss{Ao, if this is from McCall, we should just cite
    the primary source and remove the Van Vliet reference.}
\end{defn}

@@

\begin{defn}
  The ability to link software components to requirements
  \citep{McCallEtAl1977}. (As summarized in \citet{VanVliet2000}.)
\end{defn} \wss{Once we have verified McCall, we can remove the Van Vliet
  reference.}

@@

Verifiability is related to testability, which is defined by McCall et al.\ as
``The effort required to test a program to ensure that it performs its intended
function'' \citep{VanVliet2000}. \wss{Need to verify McCall reference, then
  delete VanVliet.}
